 \chapter{Metrics for Analysis}
\section{Independent Variables}


\section{Emotional Coding}
For the emotional coding of news articles, we use dictionaries from the Harvard General Inquirer, a lexicon that is popular for computerized content analysis \cite{ stone1963computer}. The Inquirer is a public-use alternative to the LIWC system, which in Berger and Milkman’s study of online virality showed results that were significantly positively correlated with the output of manual coding \cite{berger2012makes}. In particular, we use the \emph{Positiv} and \emph{Negativ} collections, a set of 1,915 well-established words signifying positive outlook (not including words for \emph{yes}) and 2,291 words signifying negative outlook (not including words for \emph{no}), respectively. Repeating the same metrics from \emph{What Makes Online Content Viral?}, we quantify for each document:

$$ emotionality = \frac{count(positiv \mid negativ)}{count(words)}$$
$$ positivity = \frac{count(positiv)}{count(words)} - \frac{count(negativ)}{count(words)}$$

as independent variables in our analysis.

 \section{Followership as a Proxy for Political Engagement}
In the following sections, we use Twitter followership as a proxy for measuring degrees of political engagement. 

Previous research in network analysis and attempts to predict latent political affiliations of users in the social network has shown that users on Twitter tend to show network homophily within political groups, and that ``like follows like'' \cite{colleoni2014echo}. In addition, followership of only Democratic or only Republican official accounts can be used as a reasonable estimator of party loyalty. Those accounts that follow only the officials of one party tend to demonstrate more closeness with other users in their political party than those who do not.
            
Due to the highly individual nature of this election, where candidate loyalty does not necessarily imply goodwill towards the party, we look specifically at what candidates users follow instead of party loyalty at large. 

For \emph{levels} of political engagement, we group those Twitter users who share news stories into three segments: 

\begin{itemize}
  \item \emph{the unaffiliated} (those who follow no presidential candidates, but do tweet about political news)
  \item \emph{single-candidate} Tweeters (those who follow one and only one presidential candidate, and tweet about political news)
  \item \emph{political aficionados} (those who follow all 4 (or more) candidates, and tweet about political news)
\end{itemize}

In addition, for single-candidate Tweeters, we divide users by the candidate they follow. At the time of data collection completion (May 1, 2016), the top two candidates by delegate count in each party were Hillary Clinton (D), Bernie Sanders (D) and Donald Trump (R) and Ted Cruz (R), so we split users into these four groups. We call each group \emph{X}-followers where \emph{X} is the candidate name, although these do not include every person on Twitter who follows \emph{X}.  


\subsection{Who Are Single-Candidate Tweeters?}
A qualitative peek into the characteristics of single-candidate tweeters shows a reasonable proxy for candidate loyalty. Examining the top 10 followers for each candidate by volume of tweets shared by each in our dataset, we see a mix of personal, organizational, and other accounts.

Below is a random sample of the profile descriptions of 10 single-candidate tweeters (usernames excluded for the sake of privacy):
 
\begin{itemize}  

\item\emph{Clinton follower}: I write about climate change, Nikola Tesla, and Abraham Lincoln. Oh, and I'm an aquarium nut. Go figure.

\item\emph{Trump follower}: Trump supporter, free-lance writer, loves life, liberty \& the pursuit of happiness

\item \emph{Sanders follower}: I am an Android. MUST NOT SLEEP; MUST WARN OTHERS

\item \emph{Clinton follower}: Love a little political humor? Then Letters From Us is the site for you. Check us out for new daily blogs and comics to feed your left-brain.

\item \emph{Trump follower}: I am a former Marine (E-5 Sergeant.)I am a proponent of eradicating a welfare state.  I am appalled by the degradation of society by the liberal establishment
 
\item \emph{Trump follower}: We bring you the biggest breaking stories all over the world. We have online journalists that are experienced \& caffeinated. with @JoshiiHD \& DaviiHD
 
\item \emph{Clinton follower}: Media Critic/Journalist/Hillary 4 Am. Vol. Leader ~Prolific!!! Bad Manners Blocked! Blogs: https://t.co/KraI7CJNlD \& https://t.co/WRcDx0bP63 \#PDMFNB \#UniteBlue
 
\item \emph{Sanders follower}: I am not accepting new clients. I am on vacation and not eligible to practice law until July 15, 2016.

\item \emph{Clinton follower}: Graduate of Delaware State, U of Penn, Bowie Md and Temple U

\item \emph{Cruz follower}: Conservative, Christian, Farm wife to @1861\_again, Stay at home mom of 3 boys, Gardner, Altrium health suppliment dealer, Strict Constitutionalist, Former Nurse

\end{itemize}



%  \chapter{The Electome Project}
%  % intro-y to electome here
%  % cite its outcomes 
 

% \section{Motivation}
% \section{Approach}
% \section{Applications}