%% This is an example first chapter.  You should put chapter/appendix that you
%% write into a separate file, and add a line \include{yourfilename} to
%% main.tex, where `yourfilename.tex' is the name of the chapter/appendix file.
%% You can process specific files by typing their names in at the 
%% \files=
%% prompt when you run the file main.tex through LaTeX.

\chapter{Introduction} 

Does anyone trust the news anymore? Not according to the latest Gallup Poll, which showed that only 4 in 10 Americans believe that mass media does a good job of reporting the news ``fully, fairly, and accurately.'' It's a major decline since the poll was first taken in 1999, back when more than half (55\%) of Americans believed the news was trustworthy \cite{Gallup-trust-2015}.

And the trend has been steadily downward: in short, the majority of Americans have had little to no trust in mass media news coverage since 2007: a discouraging view for a tumultuous time in journalism.

But beyond frustrated readers and reporters, why does distrust in the news matter? For one, media bias---or at the very least, the \emph{belief of} a biased media bias---may have a significant impact on the practice of democracy. A 2006 study from Georgetown University shows that those with more negative attitudes towards the news tend to be more highly influenced by their partisan prior beliefs and less by contemporary issues and messages when voting \cite{ladd2005attitudes}. This implies that distrust of media plays a large role in the polarization of American politics.


%In light of the upcoming 2016 U.S. elections, perceptions of media bias are of especially high stake. It has been shown that belief in media tends to plummet in election years, and claims of media bias and favoritism are already running rampant \cite{Gallup-trust-2015}. Analysis at the New York Times showed that the news media gave Republican candidate Donald Trump a \$1.9 billion advantage in free publicity, an amount 190 times as much as paid advertising \cite{Trump-advantage}.

  

%Although the general consensus of mistrust is clear, perception of media bias is a complex phenomenon to dissect, as it combines social and psychological effects with the traits of the story itself.


In light of the upcoming 2016 elections, this thesis explores perceptions of media trust and fairness in coverage of the presidential candidates. Claims of media bias and favoritism are especially high-stakes in election years, where trust has been shown to plummet \cite{Gallup-trust-2015}. And in this election cycle, cries of bias have been especially loud: Analysis at the New York Times showed that the news media gave Republican candidate Donald Trump a \$1.9 billion advantage in free publicity, an amount 190 times as much as paid advertising \cite{Trump-advantage}.

In this thesis, we examine some of the factors that contribute to the perception of media bias. In particular, how does the \emph{content} of a story (reading level and vocabulary) affect the reader versus the \emph{context} (publication and author)? 

We break down the larger question of media bias in two dimensions: trust and fairness in reporting, and examine the role of language in influencing the reader.  Although studies have been conducted to both examine the psychological effect of wording on believability and the impact of media brands and bias, separating and comparing these two factors remains largely unexamined \cite{weisberg2008seductive, baum2008eye}

Two studies are performed: a preliminary and main experiment to collect reader's perceptions of news stories through crowdsourcing. We manipulate the source of the story to examine effects of media brands on the reader, and also compare trust and fairness rankings between high and low reading level stories.

Although the general consensus of mistrust is clear, perception of media bias is a complex phenomenon to dissect, as it combines social and psychological effects with the traits of the story itself. This thesis hopes to shed new light on understanding what motivates readers' trust and distrust of news media.


 
%To begin with, whether or not we see news as biased is biased in itself. On whole, conservative readers tend to view media as more biased than both Democrats and Independents (49\% to 32\% and 35\%, respectively)\cite{Pew-bias-2012}. Partisans have also been shown in experiment to view the news as antagonistic to their beliefs, a phenomenon known as the ``hostile media effect'' \cite{vallone1985hostile}. To further complicate issues, attempting to measure a story's ``true'' subjectivity is a slippery task. Can it ever be possible to measure subjectivity in an objective matter?
 
%Yet the perception of media bias---regardless of ground truth---has a significant impact on the public. It can affect attitudes towards the government and even change voting outcomes, as measured by the impact of introducing Fox News in the cable market (it led to a significant effect on the share of Republican votes in targeted areas) \cite{dellavigna2006fox}.

%In light of the upcoming 2016 elections, this thesis explores perceptions of media bias towards presidential candidates. In particular, how does the \emph{content} of a story (reading level and vocabulary) affect the reader versus the \emph{context} (publication and author)? Although studies have been conducted to both examine the psychological effect of wording on believability and the impact of media brands and bias, separating and comparing these two factors remains largely unexamined \cite{weisberg2008seductive, baum2008eye}

%The first part of this thesis consists of a crowdsourcing experiment to collect reader
%'s perceptions of candidate bias. In this section, we use A/B testing to measure the effect of viewing the source of a story and its context. We follow up with an analysis of story reading level, language and its impact.
 